Subject-specific curves for time series forecasting of smart meter demand

### 2020-01-30 sscts-paper-1-wp.Rmd
Add formulas for CV statistic and error measures.

We use the pooled linear regression model for feature selection as it is quick to fit using ordinary least squares and allows us to model buildings by using a dummy variable for each. Using a linear model also has the advantage of allowing us to efficiently compute the leave-one-out cross-validation (LOOCV) scores [@Seber2012-gu]. Training data is comprised of business days within a window of `r fcst_train_window` days prior to the month we wish to select variables for. As our experimental setup for the validation phase involves one-day ahead forecasts, this variable selection prevents us from using any data from the future. For example, when forecasting for any date in January, only data from the months preceding January would have been used to select predictors.

@@

  1. Mean absolute error (MAE).
  2. Mean absolute percentage error (MAPE).
  3. Symmetric mean absolute percentage error (sMAPE).
  4. Mean absolute scaled error (MASE).

These are all well established forecasting metrics. Advantages and disadvantages of each are well described in @Hyndman2006-bp.

>>>>

We use the pooled linear regression model for feature selection as it is quick to fit using ordinary least squares and allows us to model buildings by using a dummy variable for each. Using a linear model also has the advantage of allowing us to efficiently compute the leave-one-out cross-validation (LOOCV) scores using [@Seber2012-gu]

$$
\text{CV} = \frac{1}{n} \sum_{i=1}^n \left(\frac{e_i}{1-h_i}\right)^2,
$$

where $e_i$ are the residuals of the model and $h_i$ are the diagonal elements of the hat-matrix $\mathbf{H} = \mathbf{X} \left( \mathbf{X}' \mathbf{X}  \right)^{-1} \mathbf{X}'$.

Training data is comprised of business days within a window of `r fcst_train_window` days prior to the month we wish to select variables for. As our experimental setup for the validation phase involves one-day ahead forecasts, this variable selection prevents us from using any data from the future. For example, when forecasting for any date in January, only data from the months preceding January would have been used to select predictors.

@@

1. Mean absolute error: $\text{MAE} = \text{mean} \left( | y_t - \hat{y}_t | \right)$.
2. Mean absolute percentage error: $\text{MAPE} = \text{mean} \left( \left| \frac{100(y_t - \hat{y}_t)}{y_t} \right| \right)$.
3. Symmetric mean absolute percentage error: $\text{sMAPE} = \text{mean} \left( \frac{200 |y_t - \hat{y}_t| }{y_t + \hat{y}_t} \right)$.
4. Mean absolute scaled error: $\text{MASE} = \text{mean} \left( \left| \frac{y_t - \hat{y}_t}{ \text{mean} ( | y_t - y_{t-1} |)} \right| \right)$.

These are all well established forecasting metrics. Advantages and disadvantages of each are described in @Hyndman2006-bp.
